\documentclass{icmmcm}

\usepackage{url}
\usepackage{graphicx}
%\usepackage{listings}

\newcommand{\der}{\mathrm{d}}

\title{The Mathematical Model of the Optimized Use of Ebola Virus Drug}
\team{38403}
\question{A}
%\date{February 8, 2015}

\begin{document}
\begin{summary}
As we all know, a new medication could stop Ebola and cure
patients whose disease is not advanced. So how can we make full
use the value of new medication? We will build two models:
one mathematical model about Ebola virus infection trends,
isolate time and the amount of the drug, another mathematical
model to explore the optimal allocation of transportation 
systems and drug production rate.
\par Model one: the mathematical model about Ebola virus
infection trends and isolate time and the amount of the drug.
According to the characteristics of Ebola virus transmission,
we model the spread of the Ebola virus Ordinary Differential
Equation(ODE) and the draw the relevant graphics. With the help
of phase trajectories nature, we can not only discuss the
nature of ordinary differential equations model with the spread
of the Ebola virus, but also describe the entire process of
Ebola virus transmission and calculates the best time to 
Ebola virus isolation initially.
To analyze the usefulness of the model, we use nonlinear
regression function to calculate the data  to verify the
reliability of the model.
\par Model two: explore optimal allocation of transport systems 
and drug production rate. According to the practical
application of the Ebola virus drug, we establish some special
mathematical models,which were analyzed using linear
programming, so that drug transport is simple and fast,
saving the transportation time.
\end{summary}

\maketitle
\thispagestyle{fancy}

%%% Uncomment the following lines if you have figures or tables in
%%% your report:
%% \listoffigures
%% \listoftables

\section{Introduction}
\subsection{The basic situation of Ebola virus}
Ebola virus can cause humans and primates producing blood, with
a high mortality rate of approximately 50\% to 90\% \cite{bib1},
effective drugs will be developed when the task. World Medical
Association declared that the development of drugs can cure
patients whose illness is not serious, so how to make full
use of the drug is the important factor when we establish
model.
\subsection{The Direction of Research}
The main direction of our research is to use a variety of
mathematical methods and means to achieve the optimal use 
of the drug and the full value of drug, thereby reducing the
Ebola virus infection rate and mortality.
\section{Problem Analysis}
\subsection{The Restatement of the Problem}
Ebola virus appeared resulted in the death of many patients,
the Medical Association developed a drug to cure patients yet
to come late, so that more patients get second chance to see
the hope of life.
\par Our  model is  consistent with the value of the drug.
\par Factors that play a crucial role in the influence of drugs,
including the speed of the disease, isolation time, the amount
of drug required drug, delivery systems and drug production
speed. Thus our tasks are gradually clear.
The task is as follows:
\begin{itemize}
  \item The establishment of the model one is to be more
  intuitive to see the trends in the spread of Ebola virus.The
  model not only provides important information for Ebola
  virus' prevention and treatment but also a similar model for
  the spread of other virus.
  \item Using the conclusion of model one, we can calculate the
  isolation time roughly and then calculated the drug dosage
  further.
  \item Finding the number of Ebola virus infection in past
  data, and then we use nonlinear regression function
  ``nlinfit'' to validate the model one.
  \item The establishment of the model two is to explore the
  best transportation system for drug distribution, so that we
  can save drug delivery time and strive to save more patients.
  \item Using the model two elaborating the drug delivery rate
  and drug production speed is to calculate vaccines and drugs
  production speed.
  \item Write a non-technical letter for the World Medical 
  Association's announcement.
\end{itemize}
\subsection{The Layout of Problem Solving}
\begin{itemize}
  \item First of all, we need to establish the ordinary
  differential equation models of the spread of Ebola
  virus(model in Section~\ref{sec:m1}), draw images, describe
  propagation of Ebola virus and discuss the characteristics
  concerned the solution. At the same time, using of the model
  we can calculate the best time to isolate rough.
  \item Secondly, use the results of model one to identify
  positive relationship between dosage and the number of
  infections including time parameter variables, and then we
  can calculate the total dose.
  \item Thirdly, according to the Ebola virus infection data provided
  by the World Health Organization, we draw a scatter plot and
  use nonlinear regression function to analyze the reliability
  of the model.
  \item Fourthly, using linear programming model in the use of
  transport,we establish transport system of Ebola drug.
  \item Fifthly, using the model two about the optimization result of
  drug transport, we can identify the nonlinear relationship
  between the production rate and drug dispensing transport
  optimal results and calculate the speed of vaccines and drugs
  production.
  \item Finally, according to the results of our research,
  write a non-professional letter for the World Medical
  Association's announcement.
\end{itemize}

\section{Model Design}
\subsection{The Spread of the Ebola Virus}
\label{sec:m1}
\input{m1spread}
\subsection{Required Drug}
\input{m1demand}
\subsection{Transportation System}
\input{m2trans}
\subsection{Produnction Speed}
\input{m4output}
\section{Testing and Analysis}
\input{mtest}

\section{Model Evaluation}
\subsection{Advantage}
\begin{itemize}
  \item This model gives a result of a general, not only for
  Ebola virus infection case analysis, but also for other
  infections virus analysis.
  \item Model use a method of combination of numbers and shapes
  to present Ebola virus propagation visually objectively.
  \item Model了not only takes into account more than two origin,
  more requirements to the case  but also combines drug
  production speed with drug delivery speed to get the optimal
  allocation scheme.
  \item In the modeling process, we fully consider the patient
  cured or deaths are no longer contagious, greatly improving
  the accuracy of the model and the ability to improve the
  application of the model.
  \item The principle of the model is straightforward. It
  simplify algorithm. Model has good practicability.
\end{itemize}
\subsection{Weaknesses}
\begin{itemize}
  \item The study population N is the total number of dynamic
  change, there is birth, death, flow and so on. This makes the
  model and the actual situation have a tolerance.
  \item Ebola virus in the human body have latency and Ebola
  virus carriers is not contagious, and this is where the model
  is not perfect.
  \item  Drug has half-life in human body. Patients must adhere
  to medication for some time to recover, so the dose
  calculations and the actual have a tolerance.
  \item model does not take into account the differences of
  each drug production's technologies and the speed of
  manufacturing of the drug. In addition, Transport can be
  selected arbitrarily and the difficulty of journeys of local
  productions of drug to where needed drug are different. These
  make the best scheme of drug distribution transportation and
  the actual have a tolerance.
  \item Under actual conditions, There are times when the drug
  production and transit of products and patients taking the
  drug during a certain waste so there is a tolerance of drug
  production speed with the actual situation.
\end{itemize}
\subsection{Improvement and Value of the Model}
In the process of model predictions, program one in model one
ignores many factors, does not comply with the later development
of Ebola virus infection. Based on program one, we consider more
factors and then establish program two. Development of Ebola
virus infection and the development of other infections were
similar. However we know that both the use of drug and isolation
measures for Ebola virus infection trend have important
effect. Therefore, our model takes into account the factors more
comprehensively. Combining with reality, we develop model which
is more consistent with the facts. In other words, under certain
circumstances our model of Ebola virus infections prediction is
accurate, but due to various factors such as variation of the
virus, it may not be able to accurately predict the long-term
trend of Ebola virus infection. To develop in line with the
actual situation of the Ebola virus-term forecast, we must
improve the above model further.
\par Model two are simplified in many factors, so our model
should consider all factors affecting the transport logistics
and distribution, but the reality is very complex,multifaceted
consideration is needed to improve our model of development
direction.
\par Through new Ebola cases elaborated each time people can
understand the strength of the infectious diseases, but they can
not see the trend of infectious diseases visually. The model we
established can solve this problem, making people realize the
Ebola virus infection trends more intuitively and seize the
best opportunity to isolate. When it comes to the transportation
systems of drug distribution, the model is able to find  the
shortest time of transportation and production. Thus saving more
time, providing the drug to the places needed drugs in time,we
can save more people. Our model can be applied not only to the
establishment of the Ebola virus, but also be applied to a virus
similar to Ebola.

\section{A Letter for the World Medical Association}
\centerline{A letter for the World Medical Association}
Dear the World Medical Association:
\par Thanks to the world medical association has manufactured a
new medication for the treatment of Ebola virus to control the
spread of Ebola, more and more patients can be treated. In
order to make better use of the medication, we also need to
optimize the amount of drugs, drug distribution transportation
systems, drug production speed.
\par According to our research, in terms of the development
trends of  Ebola virus infection, if a disease outbreak early
without any human control, Ebola cases will continue to
increase dramatically. However, after the artificially
controlled, e.g., therapeutic agents, when used for drug
optimization, Ebola cases increased trend has control, even
evolve into decline. We also found that if the number of
infected people exceeds to a certain value, infectious diseases
will spread. when high population density, density infected
people lack the necessary precautions to isolate patients to
take bad treatment, contact rate large population, excluding
rate is relatively high, the Ebola virus will spread potential
was fast. So when people are in high population density
environment, and the lack of the necessary precautions, contact
rate and large population, excluding rate is relatively high,
the Ebola virus's spread potential was fast. On the contrary,
when people are in an environment with low population density
and the governments have better preventive measures, it can
effectively control the spread of the Ebola virus. In terms of
drug dosage, we want to ensure that not only each patient whose
disease is not advanced has enough drugs to treat, but also
strive to drug waste as little as possible. We use the most
severe cases of illness required does as the base, the base
multiplied by the number of patients is the best dose.
\par We also studied the best drug distribution transport
systems. This program is not only to make sure each drug needs
to have sufficient amount of drugs, but also in the shortest
time available. Therefore, when required in each drug dose to
the needs and capacity of each dose of origin are a constant
premise, we have come to a certain percentage of the
production of various origin drugs and drug transport to
various places of the time required to reach the minimum, this
allocation transportation system drug distribution is the best
transportation system. This transport system can save more time
to control the spread of the disease and save more lives. In
terms of drug production speed, transported to where the
production of each dose of medicament required by dividing the
time required for the production of the amount of drug is the
best speed of manufacturing of the drug. Mentioned above is the
result of our study. We hope that the World Medical Association
will seriously consider and adopt the results of our study, and
show an announcement on better optimize the use of drugs in
order to do a better job in the fight against Ebola!
\par Our team wishes Ebola patients can recover rapidly and
people all around the world are happy and healthy!\\\nline%
\rightline{Team \#38403}
\rightline{February 9, 2015}

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{bib1}Ebola virus, Baidu Encyclopedia,
  \url{http://baike.baidu.com/subview/188032/5072671.htm}

\bibitem{bib2}Wei Li, On Mathematical Model of the Spread of
  SARS Virus, Journal of Bijie Teachers College (volume 22,
  issue 2, June 2004)

\bibitem{bib3}Jiang Hua,Pan Haixia,\ldots, Simulating the Ebola
virus disease transmission and outbreak in China by using computational
epidemiological model, Chinese Journal of emergency
medicine(volume 23, issue 9, September 2014)

\bibitem{bib4}Xueqin Wu,Linear Programming in logistics and
transportand application of mathematical models, Journal of
Jiangxi Vocational and Technical College of Electricity(volume
20, issue 1, March 2007)

\bibitem{bib5}The latest data of deaths from Ebola,
\url{http://snap.windin.com/ns/findsnap.php?id=232970537}

\bibitem{bib6}Shaohui Zhang, The mathematical model, Science
Press(August 2010)
\end{thebibliography}

\section*{Appendix}
\input{appendix}

\end{document}
